\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, hmargin=0.75in, vmargin=1in]{geometry}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{lipsum}
\usepackage{vwcol}
\usepackage{hyperref}
\usepackage[letterspace=-50]{microtype}
\definecolor{shadecolor}{rgb}{0.76,0.76,0.76}
\setlength{\parindent}{0cm}

\newcommand{\ts}{\textsuperscript}

\begin{document}

% Removes page numbering
\pagenumbering{gobble}

%---------------------------------------%
% Title and Contact Info
%---------------------------------------%
\hfill
\makebox[0.4\linewidth][c]{
    \parbox{1.35\paperwidth}{
        \vspace{-3mm}
        \begin{shaded*}
            {\Huge\bf Joshua Allum}\par
            {\tt\small https://jtaaa.github.io}\par
            {\tt\small joshuatallum@gmail.com $|$ 647-701-9615}
        \end{shaded*}}} \par


\begin{minipage}[t]{0.35\textwidth}

%---------------------------------------%
% Education
%---------------------------------------%
{\LARGE\sc - Education -} \smallskip\par
{\large\sffamily\bf University of Waterloo}\\
{\fontfamily{qag}\selectfont 
Honours Computer Science\par
\footnotesize Expected April 2020.\par
\small\fontfamily{bch}\selectfont
Dean's Honours List: Fall 2016\\\bf
Cumulative Average: 88.80\%\\
Faculty/Major Average: 94.33\%}
\smallskip

{\large\sffamily\bf St. Mary's College} \par
{\small\fontfamily{bch}\selectfont\small Graduated in May 2015\\Achieved 10 grade 1's in CAPE.}
\bigskip


%---------------------------------------%
% Skills
%---------------------------------------%
{\LARGE\sc - Skills -} \smallskip\par
{\large\sffamily\bf Proficient in: \par}
{\small\fontfamily{qag}\selectfont C, C++, JavaScript, HTML, Racket, Git\par Microsoft Excel, Word, \LaTeX.}\par
{\large\sffamily\bf Familiar with: \par}
{\small\fontfamily{qag}\selectfont PHP, Python, Android, Java, Microsoft Access.}\par
{\large\sffamily\bf Learning: \par}
{\small\fontfamily{qag}\selectfont MySQL, Sequel, R}\par
\bigskip


%---------------------------------------%
% Achievements
%---------------------------------------%
{\LARGE\sc - Achievements -} \smallskip\par
{\footnotesize\sffamily\bf 2013 $|$ {\small10\ts{th} overall in the Caribbean}}\par
{\small\fontfamily{qag}\selectfont CAPE, Computer Science Unit 1.}\par
{\footnotesize\sffamily\bf 2013 $|$ {\small Chief Scout Award}}\par
{\small\fontfamily{qag}\selectfont Awarded by the President of Trinidad \& Tobago.}\par
{\footnotesize\sffamily\bf 2015 $|$ {\small National Scholarship Winner}}\par
{\small\fontfamily{qag}\selectfont Awarded based on exceptional performance in CAPE.}\par
{\footnotesize\sffamily\bf 2012-16 $|$ {\small Music Festival Champions}}\par
{\small\fontfamily{qag}\selectfont Winner with the Holistic Music School Ensemble of the biannual T\&T Music Festival three times consecutively.}\par
{\footnotesize\sffamily\bf 2014 $|$ {\small 23\ts{rd} World Scout Jamboree}}\par
{\small\fontfamily{qag}\selectfont Represented Trinidad \& Tobago internationally at the 23\ts{rd} WSJ in Japan.}
\bigskip

\vspace{10mm}
{\sffamily\bf 2013-15 $|$ {\large CS Club}}\par
{\small\fontfamily{qag}\selectfont Executive member of the St. Mary's College Computer science club.}

%---------------------------------------%
% Links
%---------------------------------------%
\makebox[0.67\linewidth][c]{
    \parbox{0.38\paperwidth}{
        \begin{shaded*}
            \hspace{0.6in}{\LARGE\sc Links} \smallskip\par
            \hspace{0.3in}{\small\sffamily\sc GitHub \hspace{2.12mm}$|$ {\tt\normalsize\lsstyle \href{https://github.com/jtaaa}{github.com/jtaaa}}}\par
            \hspace{0.3in}{\small\sffamily\sc LinkedIn $|$ {\tt\normalsize\lsstyle \href{https://www.linkedin.com/in/joshua-allum/}{linkedin.com/in/joshua-allum}}}\par
        \end{shaded*}}}

\end{minipage}
\hfill
\begin{minipage}[t]{0.63\textwidth}

%---------------------------------------%
% Work Experience
%---------------------------------------%
{\LARGE\sc - Work Experience -} \smallskip\par
{\large\sffamily\bf Western Union} $|$
{\small\sffamily\lsstyle Front Line Agent, Sept 2015 - May 2016} \par
{\small\fontfamily{qag}\selectfont\textbullet\ Handled money transactions of hundreds of clients per week.\\
\textbullet\ Created excel spreadsheets to record daily transactions and produce predicted balance figures.}
\smallskip

{\large\sffamily\bf Quivira Scout Ranch} $|$
{\small\sffamily\lsstyle International Camp Counselor, June 2016} \par
{\small\fontfamily{qag}\selectfont\textbullet\ Taught young scouts about scouting, specifically rowing, kayaking, motor-boating and sailing.
\\\textbullet\  Collaborated with the management of QSR and the scouting association of Kansas to inform Kansan scouts of the world beyond the USA.} \par
\bigskip

%---------------------------------------%
% Projects
%---------------------------------------%
{\LARGE\sc - Projects -} \smallskip\par
{\sffamily\bf\small {\large Carnival Band Database $|$} Microsoft Access}\par
{\small\fontfamily{qag}\selectfont\textbullet\ Designed a database to manage a carnival band's member data.\\
\textbullet\ Included multiple forms, reports and mail merge features to sign up new masqueraders, show statistical data and distribute personalized band information to members.\\
\textbullet\ Integrated with Microsoft Excel and Office to facilitate easy data input and information output in the form of charts and graphs.}
\medskip

{\sffamily\bf\small {\large Heart Rate Calculator $|$} C}\par
{\small\fontfamily{qag}\selectfont\textbullet\ Designed and coded from scratch a C program that computes, stores and manages the average heart rates of users. \\
\textbullet\ Features include data storage and management in a custom encoded file and warning messages for abnormal heart rates.\\
\textbullet\ Fitness level is calculated by checking user heartrate against the average heart rate of a person in the user's demographic.}\par
\medskip

{\sffamily\bf\small {\large Connect Web-app $|$} HTML, CSS, PHP}\par
{\small\fontfamily{qag}\selectfont\textbullet\ A collaboration with a team of four to create a web-app that stores a set of user-defined hyperlinks and generates a unique web-page, with the user's links embedded, that can be shared.\\
\textbullet\ I took on the back-end and learnt PHP on the spot in order to store user links in a .txt file and generate page URLs.}\par
\bigskip


%---------------------------------------%
% Ongoing Projects
%---------------------------------------%
{\LARGE\sc - Ongoing Projects -} \smallskip\par
{\sffamily\bf\small {\large CapeNotes.com $|$} HTML, CSS, PHP, JavaScript}\par
{\small\fontfamily{qag}\selectfont\textbullet\ Working in my spare time on a website that provides CAPE students with course notes, practice questions and a list of relevant materials.}\par
\bigskip


%---------------------------------------%
% Clubs & Activities
%---------------------------------------%
\hspace{-6.5cm}{\LARGE\sc - Clubs\hspace{1.8cm} \&\hspace{1.8cm} Activities -} \smallskip\par
{\sffamily\bf 2009-15 $|$ {\large First Trinidad Sea Scouts}}\par
{\small\fontfamily{qag}\selectfont Troop Leader tasked with planning and organizing events.\\
40+ hours of community work includes beach clean ups, charity events and life guarding services.}\par
{\sffamily\bf 2009-15 $|$ {\large Holistic Music School Ensemble}}\par
{\small\fontfamily{qag}\selectfont Semi-professional lead flautist in a mainly
jazz but also folk and locally oriented band.}\par
{\sffamily\bf 2013-14 $|$ {\large Management Team}}\par
{\small\fontfamily{qag}\selectfont Member of the St. Mary's College M-Team that plans and organizes school events such as fundraisers and external functions.}\par

\end{minipage}


\end{document}
